CSCI 580 : Monte Carlo Path Tracing

### 2015-12-02 paper/paper.tex

\section{Introduction}
Rendering via the use of rays, such as in the Monte Carlo path tracing approach, stands in stark contrast to the rasterization of triangles, which is the faster and more common approach to rendering, and the one used throughout the assignments of the CSCI 580 course. However, with path tracing it is possible to achieve photorealism by simulating the travel of photons, rather than the approximations used in renderers that make use of rasterization. INSERT STUFF RELATING TO WHAT WE ACCOMPLISHED.

@@

\begin{description}
  \item[1)] Generate a ray from the camera (position x,y, horizontal and vertical fields of view u,v), passing through the image plane, with weight = 1
  \item[2)] Find the point of intersection with the nearest surface
  \item[3)] Randomly (Russian Roulette) decide whether the light is emitted or reflected (test against this random number against the Kd of the surface):
  \item[3A)] if emitted, return weight * shading from light source(s)
  \item[3B)] if reflected, weight *= Ks, randomly scatter the ray according to a probability density function (pdf) approximating its bidirectional refletance distribution function (brdf), and go to step 2
\end{description}

@@

\section{Implementation}
Explain architectural changes.
Explain what parts of Monte Carlo we did.

>>>>

\section{Introduction}
Rendering via the use of rays, such as in the Monte Carlo path tracing approach, stands in stark contrast to the rasterization of triangles, which is the faster and more common approach to rendering, and the one used throughout the assignments of the CSCI 580 course. However, with path tracing it is possible to achieve photorealism by simulating the travel of light, which bounces off surfaces, resulting in shadows, specular as well as diffuse reflections andrefractions rather than the surface shading approach used in renderers that make use of rasterization.

@@

\begin{description}
  \item[1)] Generate a ray from the camera (position x,y, horizontal and vertical fields of view u,v), passing through the image plane, with $weight = 1$
  \item[2)] Find the point of intersection with the nearest surface
  \item[3)] Randomly (Russian Roulette) decide whether the light is emitted or reflected (test against this random number against the Kd of the surface):
  \item[3A)] if emitted, return $weight * shading$ from light source(s)
  \item[3B)] if reflected, $weight \mathrel{*}= Ks$, randomly scatter the ray according to a probability density function (pdf) approximating its bidirectional refletance distribution function (brdf), and go to step 2
\end{description}

@@

\section{Implementation}
Firstly, we used the codebase of the previous assignments as a launching point for the project. Thus, the GUI and initialization, as well other elements such as the rendering parameters, the functions for displaying pixels to the screen and a number of vector and matrix functions were borrowed directly from previous assignments. However, rasterization-related functionality was thrown out and replaced with an entirely new way of rendering via rays.
\par
The graphics pipeline was designed as follows: initialization is carried out, wherein global properties such as camera position and lights are defined. Then, the meshes are loaded into memory as a data structure encompassing all triangles. Each vertex in the triangle has a position, a normal, as well as information on their specular, diffuse and ambient coefficients, which differs from the global Ks, Kd and Ka found in the assignment renderer.

\par
asda
